Model LF

### 2022-12-21 Estimation.Rmd
Commit

```{r}
urca_lf= ur.df(g_lf, lags = 1, type = "none")
summary(urca_lf)
```

@@

```{r}
"COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) = p_520 + p_522* TSDELTA(TSLAG(ur,4)) + p_523* TSDELTALOG(prod_ds) + p_524* LOG(TSLAG(wage_ds,1)) + p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1)) + p_527* (d_2009q1 + d_2009q2)
COEFF> p_520 p_522 p_523 p_524 p_525 p_526 p_527 
STORE> coe(20)"
```

@@

test_dummy= d_2009q1 + d_2009q2 
reg_wage_ds_start=dynlm(TSDELTALOG(wage_ds) ~ 1+ L(TSDELTA(wage_ds), 1:4) + L(TSDELTA(ur), 0:4)+ L(TSDELTALOG(prod_ds), 0:4) + L(wage_ratio, 0)+  L(log(wage_ds_t), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + test_dummy)

@@

```{r}
reg_wage_ds=dynlm(TSDELTALOG(wage_ds) ~ 0 + L(TSDELTA(ur), 1)+ L(TSDELTALOG(prod_ds), 0)+ L(TSDELTALOG(mean_dp_regul), 2)+  L(log(wage_ds_t), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + (log(TSLAG(mean_dp_regul,1)):dummy_test) + test_dummy )

@@

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),c(1:4)) + L(TSDELTA(s_h),c(0:4)) +  L(TSDELTALOG(mean_dp_regul),c(0:4))+ L(TSDELTALOG(wage_ds),c(0:4)) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(s_h,2)+ L(log(mean_dp_regul),2))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(wage_ds),c(0,1))  +  L(TSDELTALOG(y_ds),c(0,4)) + L(log(prod_ds),1)+  L(log(wage_ds),1)+ L(log(y_ds),1) + L(log(mean_dp_regul),2))

>>>>

@@

```{r}
"COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) = p_522* TSDELTA(TSLAG(ur,4)) + p_523* TSDELTALOG(prod_ds)  + p_524* LOG(TSLAG(wage_ds,1)) + p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1))  + p_527 * (d_2009q1 + d_2009q2)
COEFF> p_522 p_523 p_524 p_525 p_526 p_527
STORE> coe(20)"

@@

test_dummy= d_2009q1 + d_2009q2 
reg_wage_ds_start=dynlm(TSDELTALOG(wage_ds) ~ 1+ L(TSDELTA(wage_ds), 1:4) + L(TSDELTA(ur), 0:4)+ L(TSDELTALOG(prod_ds), 0:4) +  L(log(wage_ds_t), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + test_dummy)

@@

```{r}
reg_wage_ds=dynlm(TSDELTALOG(wage_ds) ~ 0 + L(TSDELTA(ur), c(1))+ L(TSDELTALOG(prod_ds), 0) +  L(log(wage_ds_t_nu), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + test_dummy)

@@

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),c(1:4)) + L(TSDELTA(s_h),c(0:4)) +  L(TSDELTALOG(mean_dp_regul),c(0:4))+ L(TSDELTALOG(wage_ds),c(0:4)) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+  L(log(wage_ds),1)+ L(log(y_ds),1) + L(s_h,1)+ L(log(mean_dp_regul),1))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(wage_ds),c(0))  +  L(TSDELTALOG(y_ds),c(0,4)) + L(log(prod_ds),1)+  L(log(wage_ds),1)+ L(log(y_ds),1) + L(log(mean_dp_regul),1)+ L(s_h,1))
